DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life

### 2023-10-27 manuscript/manuscript.tex
update figure 5 description

We illustrate the DateLife workflow using a family within the passeriform birds encompassing the true finches, Fringillidae, as case study. On a small example, we analysed 6 bird species, and results from each step of the workflow are shown in Figure 3. As a second example, we analysed 289 bird species in the family Fringillidae that are included in the NCBI taxonomy. The summary chronogram resulting from the DateLife analysis is shown in Figure 5, and results from previous steps of the workflow are available as Supplementary Figures.

>>>>

We illustrate the DateLife workflow using a family within the passeriform birds encompassing the true finches, Fringillidae, as case study. On a small example, we analysed 6 bird species, and results from each step of the workflow are shown in Figure 3. As a second example, we analysed 289 bird species in the family Fringillidae that are included in the NCBI taxonomy. One clade from the full summary chronogram result from the DateLife analysis is shown figure 5. The full chronogram for all 289 species and the Fresults from previous steps of the workflow are available as Supplementary Figures.
